---
title: "Homework 2: Option B Finding Communities"
output: html_notebook
---

## Part 1: Peru

```{r}
rm(list = ls())
GitLink='https://github.com/impolichetti/HW2_Repo/raw/refs/heads/main/css_G.graphml'
```

```{r}
library(igraph)
elites=read_graph(GitLink,format='graphml')
```

```{r}
summary(elites)
```

```{r}
V(elites)$name=V(elites)$id
```

```{r}
V(elites)$color[V(elites)$color == ""] <- "black"
```

```{r}
unique(V(elites)$color)
```

```{r}
set.seed(111)
plot.igraph(elites)
```

```{r}
transitivity(elites,type = "local")

```

```{r}
transitivity(elites,type = "average")

```

```{r}
clique_size_counts(elites)

```

```{r}
largest_cliques(elites)
```

```{r}
LCq=largest_cliques(elites)
par(mfrow = c(1, 3)) 
plot(elites,main='All network')
plot(induced_subgraph(elites, LCq[[1]]), main="Largest Clique  (A)")
plot(induced_subgraph(elites, LCq[[2]]), main="Largest Clique  (B)")
```

```{r}
set.seed(123)
elites_gn <- cluster_edge_betweenness(elites,directed = F)
```

```{r}
sizes(elites_gn)
```

```{r}
plot(elites_gn, elites,
     layout = layout_with_kk, 
     main="Girvan-Newman Solution")
```

```{r}
modularity(elites, membership(elites_gn),directed = FALSE)
```

### The Louvain method

```{r}
set.seed(321)

elites_lv <- cluster_louvain(elites)
sizes(elites_lv)
```

```{r}
plot(elites_lv, elites,
     layout = layout_with_kk, 
     main="Louvain Solution")
```

```{r}
modularity(elites, membership(elites_lv),directed = FALSE)
```

### The Leiden method

```{r}
elites_ld <- cluster_leiden(elites)
sizes(elites_ld)
```

```{r}
set.seed(123)
elites_ld_mod <- cluster_leiden(elites,
                              objective_function ="modularity")

sizes(elites_ld_mod)
```

```{r}
plot(elites_ld_mod, elites,
     layout = layout_with_kk, 
     main="Leiden Solution-using modularity")
```

```{r}
modularity(elites, membership(elites_ld_mod))
```

So far, the modularity for Louvain is 0.2746776 while the modularity for leiden is 0.288614. Leiden has higher modularity, yet still not very strong.

```{r}
set.seed(123)
### Higher resolutions lead to more smaller communities, 
### while lower resolutions lead to fewer larger communities.

#r = quantile(strength(actors))[2]/(gorder(actors) - 1)
r=edge_density(elites) 
elites_ld_cpm <- cluster_leiden(elites,
                              objective_function ="CPM",
                              resolution_parameter = r)

sizes(elites_ld_cpm)
```

```{r}
plot(elites_ld_cpm, elites,
     layout = layout_with_kk, 
     main="Leiden Solution-using Pots Model")
```

```{r}
modularity(elites, membership(elites_ld_cpm))
```

After testing Leiden and Louvian algorithms, we should use the leiden method since it has a larger modularity.

## Part 2: Seattle

```{r}
library(igraph)
library(CINNA)
```

```{r}
GitLink='https://github.com/impolichetti/HW2_Repo/raw/refs/heads/main/SeattleTechNetwork.graphml'
seattle=read_graph(GitLink,format='graphml')
```


### The Louvian Method

```{r}
set.seed(321)

seattle_lv <- cluster_louvain(seattle)
sizes(seattle_lv)
```

### The Leiden Method

```{r}
seattle_ld <- cluster_leiden(seattle)
sizes(seattle_ld)
```

The Louvian and the Leiden methods do not work for directed graphs.

### infomap

```{r}
seattle_giant=CINNA::giant_component_extract(seattle)[[1]]
summary(seattle_giant)
```
```{r}
set.seed(333)
sizes(cluster_edge_betweenness(seattle_giant,directed = T))
```

```{r}
set.seed(332)

seattle_info=cluster_infomap(seattle_giant)
plot(seattle_info, seattle_giant,
     vertex.label=V(seattle_giant)$country,
     layout = layout_nicely, vertex.label.cex=0.5,
     main="Infomap solution")
```

```{r}
modularity(seattle_giant, membership(seattle_info))
```
```{r}
sizes(cluster_label_prop(seattle_giant, mode = 'out'))
```
```{r}
sizes(cluster_infomap(seattle_giant))

```

### Girvan-Newmann

```{r}
set.seed(123)
seattle_gn <- cluster_edge_betweenness(seattle,directed = F)
```

```{r}
sizes(seattle_gn)
```

```{r}
plot(seattle_gn, seattle,
     layout = layout_with_kk, 
     main="Girvan-Newman Solution")
```

```{r}
modularity(seattle, membership(seattle_gn),directed = FALSE)
```


Girvan-Newman solution had a slightly higher modularity. Using this method should be chosen.

## Part 3: Fifa Country Projection

```{r}
rm(list = ls())
GitLink='https://github.com/impolichetti/HW2_Repo/raw/refs/heads/main/fifa_country_projection.graphml'

library(igraph)
fifa=read_graph(GitLink,format='graphml')

V(fifa)$name=V(fifa)$id 
```

```{r}
set.seed(111) # use this to get same results as me

plot.igraph(fifa)
```

### Girvan-Newman Method

```{r}
set.seed(123)
fifa_gn <- cluster_edge_betweenness(fifa,directed = F)
```

```{r}
sizes(fifa_gn)
```

```{r}
plot(fifa_gn, fifa,
     layout = layout_with_kk, 
     main="Girvan-Newman Solution")
```

```{r}
modularity(fifa, membership(fifa_gn),directed = FALSE)
```

### Leiden Method

```{r}
fifa_ld <- cluster_leiden(fifa)
sizes(fifa_ld)
```

```{r}
set.seed(123)
fifa_ld_mod <- cluster_leiden(fifa,
                              objective_function ="modularity")

sizes(fifa_ld_mod)
```

```{r}
plot(fifa_ld_mod, fifa,
     layout = layout_with_kk, 
     main="Leiden Solution-using modularity")
```

```{r}
modularity(fifa, membership(fifa_ld_mod))
```

The modularity for the Girvan-Newman method is 0.01644719, while the modularity for the Leiden method is 0.04542327. The higher modularity is the Leiden method, so this method should be chosen.
